---
title: "acresCOA"
author: "C A Pellett"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Using the NASS QuickStats tool, input:

## For Land numbers
Program = Census
Sector = Economics
Group = Farms & Land & Assets
Commodity = Ag Land

Data Items = 
Ag Land - Acres
Ag Land - Number of Operations
Ag Land, Cropland - Acres
Ag Land, Cropland - Number of Operations
Ag Land, Cropland, Harvested - Acres
Ag Land, Cropland, Harvested - Number of Operations
Ag Land, Cropland, Harvested, Irrigated - Acres
Ag Land, Cropland, Harvested, Irrigated - Number of Operations
Ag Land, Irrigated - Acres
Ag Land, Irrigated - Number of Operations

Domain = Total

Geographic Level = County / State

Location:
data-raw/downloaded_files/stateLandAreas
data-raw/downloaded_files/countyLandAreas

## For Crop numbers 
Program = Census
Sector = Crops
Group = Field Crops
Commodity = *Select All*
Category = Area Harvested

Geographic Level = County / State
State = *Select All*
County = Download groups of counties sequentially. The Quick Stats tool won't work with all counties selected.

Year = 2017
Period Type = Annual
Period = Year

Location:
data-raw/downloaded_files/stateFieldCropAreas
data-raw/downloaded_files/countyFieldCropAreas


## For pasture irrigation
Program = Census
Sector = Crops
Group = Field Crops
Commodity = *Select All*
Category = Area

Geographic Level = State

Location:
data-raw/downloaded_files/statePasture

## For other crops
Program = Census
Sector = Crops
Group = Fruit & Tree Nuts, Horticulture, Vegetables
Commodity = *Select All*
Category = Area bearing & non-bearing, area bearing & nonbearing, Area grown, area harvested, area in production

Geographic level = county (then do state)
state = south carolina

Location:
data-raw/downloaded_files/countyOtherCropAreas
data-raw/downloaded_files/stateOtherCropAreas


## For irrigation stats 
Program: CENSUS
Group: IRRIGATION
Geographic Level: STATE
46,256 records. nov 6, 2020


# The 2018 Irrigation and Water Management Survey

The  target  population  for  the  2018  Irrigation  and  Water  Management  Survey  was  composed  of  all  farms  irrigating  in  the  reference  year  of  2018.  The   target   population   was   expanded to include any operations that had irrigated land in the past five years.

From  the 2017 Census of Agriculture, 198,368 records were identified as belonging to the general U.S. irrigation population on the basis of having irrigation activity on their   farm   or   ranch.  

Institutional, research, and experimental  farms  were  excluded  from  the  total  number of irrigators that reported in the 2017 census. 

Data  were  collected  by  mail,  Computer-Assisted Web Interviewing (CAWI) via the Internet, telephone  enumeration,  and  personal  enumeration.  Enumeration  methods  used  in  the  2018  survey  were  similar to those used in the 2013 survey.

The report form was mailed to all the producers in the sample that reported irrigation  in  the  2017  Census  of  Agriculture.

A certainty stratum, with farms selected with probability one, was included for each State to ensure that the major irrigators in each State were  sampled.  The  remaining  strata  were  sampled  systematically by irrigated acreage. The stratification boundaries   varied   among   the   States   and   were   dependent  on  the  distribution  of  total  acres  irrigated  within the State. 

The  initial  mail  packets  were sent February 2019, and included  a  labeled  report  form,  an  instruction booklet, an instruction letter, and a return envelope. Mailout packet preparation, initial mailout, and  one  follow-up  mailing  to  nonrespondents. Telephone  follow-up began April 2019 to nonrespondents. 

Data  were  collected  for  a  select  group  of  operations  by field offices agency contacts; operations were included in  this  group  if  they  were  scheduled  for  contact  for  other  agricultural  surveys.

 The    estimation  methodology  consisted  of  two  weighting  components that made up the total survey weight. The first component was the fully adjusted weight pulled in from the 2017 Census of Agriculture. This weight accounted     for     any     list     incompleteness     and     undercoverage  from  the  2017  census.  The  second  component  was  the  sampling  rate  used  for  the  2018  Irrigation   and   Water   Management   Survey.   This   expansion  factor  was  the  inverse  of  the  selection  probability  for  the  sample  farms  in  a  stratum.  This  expansion factor was reweighted at the stratum level to    account    for    whole-farm    nonresponse.    The    nonresponse  adjustment  factor  used  to  reweight  the  expansion  factor  was  the  ratio  of  the  number  of  sample  farms  in  a  stratum  to  the  number  of  sample  farms that responded to the survey in that stratum. The assumption  underlying  this  weighting  approach  to  survey nonresponse was that survey respondents and nonrespondents    within    a    stratum    constitute    a    homogeneous  population,  thus  allowing  respondents  to represent nonrespondents.
 
 Any tabulated  item  that  identifies  data  reported  by  a  respondent   or   allows   a   respondent’s   data   to   be   accurately estimated or derived, was suppressed and coded  with  a  ‘D’.  However,  the  number  of  farms  reporting   an   item   is   not   considered   confidential   information   and   is   provided   even   though   other   information is withheld.
 
 Horticulture in the open was recorded under Other cropland during 2013 while it was recorded as its own  commodity  during  2018.  Therefore,  Other  cropland  is  not  comparable  between  2018  and  2013. 
 
 The survey includes data only for operations that irrigated  sometime  between  2013  and  2017  and  2018.  Operations  in  some  areas,  especially  the  eastern States, may irrigate only when moisture is needed.  Operations  with  irrigation  capabilities  may  not  irrigate  depending  on  the  amount  of  rainfall  for  a  particular  year  or  geographic  area. 
 
 New irrigators in 2018 (not included in the 2017 census) did not have a chance for selection in the sample  and,  therefore,  were  excluded  from  the  survey.  It  is  believed  that  the  impact  of  new  irrigators is probably minimal. 
 
 The response rate for the 2018 Irrigation  and  Water  Management  Survey  is  64.4  percent.  This  compares  to  69.8  percent  for  the  2013  Farm and Ranch Irrigation Survey.
 
 The  accuracy  of  data  products  may  be  evaluated  through   sampling   and   nonsampling   error.   The   measurement of error due to sampling in the current period  is  evaluated  by  the  coefficient  of  variation  (CV)  for  each  estimated  item.  Nonsampling  error  is  evaluated  by  response  rates  and  the  percent  of  the  estimate from respondents.  
 
 Coefficient of variation is a measure of the relative amount  of  error  associated  with  a  sample  estimate.  Specifically, it is the standard error of a point estimate divided  by  that  estimate,  generally  multiplied  times 100  so  that  it  can  be  reported  as  a  percentage.  This  relative  measure  allows  the  reliability  of  a  range  of  estimates to be compared. For example, the standard error  is  often  larger  for  large  population  estimates  than  for  small  population  estimates,  but  the  large  population   estimates   may   have   a   smaller   CV,   indicating a more reliable estimate. Every estimate for the  2018  Irrigation  and  Water  Management  Survey  has a corresponding CV published with it. 
 
 Low    Reliability    Estimate.    Coefficient    of    Variation  (CV)  30  percent  or  higher.  Caution  should  be  used  when  using  this  estimate  in  any  form. Please consult NASS for more information or guidance.  Medium  Reliability  Estimate.  Coefficient  of  Variation  (CV)  between  15  percent  and  29.9  percent  High    Reliability    Estimate.    Coefficient    of    Variation (CV) less than 15 percent.
 
 TABLE A information (South Carolina)
2017 Census of Agriculture
Published totals
Farms: 2,167
Acres irrigated: 210,437

Sample Universe (excludes institutional, educational, and research farms)
Farms: 1,597
Acres irrigated: 161,606

2018 Irrigation and Water Management Survey
Sample count
Farms: 274
2017 census irrigated acres: 74,563

Final reports processed and tabulated 
Unexpanded 
Farms: 129
Acres Irrigated: 73,298
Expanded
Farms: 1,489
Acres Irrigated: 252,720

Table C. Coefficient of Variation (percent) for Selected General Irrigation Data: 2018 (South Carolina)
Irrigated farms: 6.5%
Land in farms: 18.5
Acres irrigated (total): 33.6
Acres irrigated (cropland harvested in the open): 34.3
Acre-feet applied: 36.7
Energy expense for pumps: 33.0
Expenditure expenses: 47.5
Pumps, all types: 25.7
Well pumps: 26.3

Table D. Coefficient of Variation (percent) for Selected Horticultural Irrigation Data: 2018 (South Carolina)

Irrigated horticultural operations: 20.1%
Irrigated area, acres in the open: 73.8%
Irrigated area, square feet under protection: 85.9%



If two or more crops were  harvested  from  the  same  land  during  the  year  (double  cropping),  the  acres  were  counted  for  each  crop. Therefore, the total acres of all crops harvested could  exceed  the  acres  of  cropland  harvested.  An  exception to this procedure was hay crops.


All  other  crops.    Data  relate  to  any  non-vegetable  crops not having a specified code on the 2018 report form.  Crops  such  as  grass  seed,  sunflower  seed,  sugarcane,  etc.  were  included  in  other  field  crops.  Data are not comparable to 2013.  Horticulture acres in the open had its own category in 2018.

Cropland harvested in the open. Acres that included harvested field crops and hay along with land used for vegetables, orchards, citrus groves, vineyards, berries, nuts, cultivated Christmas trees, short-rotation woody crops, nursery and other horticultural crops grown in the  open.  Does  not  include  land  used  for  growing  horticultural  crops  under  protection  nor  cropland  reported as failed or used for cover crops.

Horticultural crops:
Cultivated Christmas trees and short rotation woody crops in the open.  Includes all trees to be cut in 2018 or  later  years.  Irrigated  live  Christmas  trees  were  reported in nursery crops. 

Floriculture  and  bedding  crops.    Includes  annual  bedding/garden  plants,  herbaceous  perennials,  cut  flowers  and  cut  cultivated  greens,  foliage  plants  for  indoor or patio use, potted flowering plants, and other floriculture type crops. 

Food crops grown under protection.  Includes all food crops that were grown in a greenhouse or under some sort    of    structure    that    regulated    light,    shade,    temperature, etc. No food crops grown in open fields were reported for this crop type.

Mushroom  crops  under  protection.    Includes  all  mushroom  species  that  were  irrigated  in  2018.  Logs  were converted to and reported in square feet.

Nursery   crops.      Includes   deciduous   shade   and   flowering trees, broadleaf and coniferous evergreens, live Christmas trees for sale as potted trees or balled and   burlapped,   fruit   and   nut   trees   and   plants,   ornamental  grasses,  palms  for  landscaping,  shrubs,  vines, aquatic plants, and other woody ornamentals. 

Propagative  materials.    Includes  dry  bulbs,  corms,  tubers,  and  rhizomes;  cuttings,  seedlings,  liners,  and  plugs;   flower   seeds;   vegetable   seeds;   vegetable   transplants; and tobacco transplants. 

Sod in the open.  Includes all irrigated sod, sprigs, or plugs. 

Other horticultural crops.  This category includes all crops  that  are  primarily  considered  ornamental  or  horticultural  and  are  not  listed  on  the  report  form.  Fruit, nut, and vegetable crops grown in the openare not considered horticultural crops.

Irrigated farms.  Irrigated farms or ranches are those with any agricultural land irrigated by any artificial or controlled  means  in  the  specific  calendar  year.  The  acreage irrigated may vary from a very small portion of the total acreage in the farm or ranch to irrigation of  all  agricultural  land  in  the  farm  or  ranch.  This  includes   reclaimed   water   and   livestock   lagoon   wastewater distributed by sprinkler or flood systems. 

Irrigated land.  Irrigated land is defined as “all land watered by artificial or controlled means.” No attempt was   made   to   define   the   degree   or   intensity   of   irrigation.   Therefore,   the   data   for   irrigated   land   include  land  with  as  little  as  one-half  inch  of  water  applied as well as land with several acre-feet of water applied. 

Reclaimed  water.    Reclaimed  water  is  wastewater  that has been treated for non-potable reuse purposes. Sources    include    municipal,    industrial,    off-farm    livestock   operations,   and   other   reclaimed   water   sources.  Water  from  off-farm  livestock  facilities,  municipal,   industrial,   and   other   reclaimed   water   sources  were  reported  as  off-farm  supplies.  While  reclaimed  water  from  on-farm  livestock  facilities  were reported as on-farm surface water.   

Recycled  water.    Recycled  water  is  the  reuse  of  surface or ground water that has already been used to irrigate  a  crop  on  the  operation.  Recycled  water  use  was reported as on-farm surface water.



```{r eval=FALSE}
z = 1

```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))





