---
title: "acresCOA"
author: "C A Pellett"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Using the NASS QuickStats tool, input:

## For Land numbers
Program = Census
Sector = Economics
Group = Farms & Land & Assets
Commodity = Ag Land

Data Items = 
Ag Land - Acres
Ag Land - Number of Operations
Ag Land, Cropland - Acres
Ag Land, Cropland - Number of Operations
Ag Land, Cropland, Harvested - Acres
Ag Land, Cropland, Harvested - Number of Operations
Ag Land, Cropland, Harvested, Irrigated - Acres
Ag Land, Cropland, Harvested, Irrigated - Number of Operations
Ag Land, Irrigated - Acres
Ag Land, Irrigated - Number of Operations

Domain = Total

Geographic Level = County / State

Location:
data-raw/downloaded_files/stateLandAreas
data-raw/downloaded_files/countyLandAreas

## For Crop numbers 
Program = Census
Sector = Crops
Group = Field Crops
Commodity = *Select All*
Category = Area Harvested

Geographic Level = County / State
State = *Select All*
County = Download groups of counties sequentially. The Quick Stats tool won't work with all counties selected.

Year = 2017
Period Type = Annual
Period = Year

Location:
data-raw/downloaded_files/stateFieldCropAreas
data-raw/downloaded_files/countyFieldCropAreas


## For pasture irrigation
Program = Census
Sector = Crops
Group = Field Crops
Commodity = *Select All*
Category = Area

Geographic Level = State

Location:
data-raw/downloaded_files/statePasture

## For other crops
Program = Census
Sector = Crops
Group = Fruit & Tree Nuts, Horticulture, Vegetables
Commodity = *Select All*
Category = Area bearing & non-bearing, area bearing & nonbearing, Area grown, area harvested, area in production

Geographic level = county (then do state)
state = south carolina

Location:
data-raw/downloaded_files/countyOtherCropAreas
data-raw/downloaded_files/stateOtherCropAreas


## For irrigation stats 
Program: CENSUS
Group: IRRIGATION
Geographic Level: STATE
46,256 records. nov 6, 2020





```{r eval=FALSE}
z = 1

```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))





